---
title: "Getting Started with binomial"
author: "Mingyue Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
```


## Binomial Experiment

The package `"binomial"` is an implementation for simulating doing a binomial experiment,
and calculating probabilities of a Binomial random variable
and related calculations such as the probability distribution, the expected value, variance, etc.


## Function bin_choose()

The `bin_choose` function use factorial() to calculates the number of combinations in which k successes can occur in n trials. The number of combinations "n choose k" is given by:
\[
    \binom{n}{k} = \frac{n!}{k!(n-k)!}
\]
The `bin_choose()` function have arguments *n* and *k*, where *k* is a vector of non-negative integer(s) less than or equal to *n*.
Below are examples of how you can invoke bin_choose(). 
```{r choose}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```


## Function bin_probability()
The function `bin_probability()` computes the probability of getting desired successes in a given number of trials.
The binomial probability is given by the formula:
\[
Pr (X = k) = \binom{n}{k}p^k(1-p)^{n-k}
\]
The function `bin_probability()` have arguments *success*, *trials*, and *prob*.
Below are examples of how you can invoke bin_probability().
```{r bin_probability}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)

# probabilities of getting 2 or less successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)

# 55 heads in 100 tosses of a loaded coin with 45% chance of heads
bin_probability(success = 55, trials = 100, prob = 0.45)


```


## Function bin_distribution()
The function `bin_distribution()` computes the probability of getting possible successes in a given number of trials.
It returns a data frame with two classes: "bindis" and "data.frame", and the data frame has
sucesses in the first column, probability in the second column.
The function `bin_distribution()` has two arguments *trials*, and *prob*.

Here is an example of how to invoke bin_distribution()
```{r distribution}
# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)
```

Function `plot.bindis()` graphs a barplot to display
the probability histogram of a binomial distribution object "bindis".
Here is an example of how to invoke the plot method.
```{r plot distribution}
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```


## Function bin_cumulative()
The function `bin_cumulative()` computes the probability distribution and cumulative probability of a binomial experiment.
It returns a data frame with two classes: "bincum" and "data.frame", and the data frame has
sucesses in the first column, probability in the second column, and cumulative in the third column.
The function `bin_cumulative()` has two arguments *trials*, and *prob*.

Here is an example o fhow to invoke bin_cumulative().
```{r cumulative}
# binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)
```

Function `plot.bincum()` graphs the cumulative distribution in an object "bincum".
Here is an example of how to invoke the plot method.
```{r plot cumulative}
# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```


## Function bin_variable()
The function `bin_variable()` return an object of class "binvar", and The returned object should be a list with named elements:
number of trials and probability of success.
The function `bin_variable()` has two arguments *trials*, and *prob*.

The method function `print.binvar()` nicely print the content of an object "binvar".
Here is an example of how you should be able to invoke bin_variable().
```{r bin_variable}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```

The method function `summary.binvar()` helps you get a full summary description of an object "binvar".
The print method function '`print.summary.binvar()` helps you nicely print the contents of an object "summary.binvar".
See example below:
```{r bin variable summary}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

## Functions of measures
These are main functions that take two arguments: trials and prob
They first check if the inputs are valid, then calculate the related measures
See examples of how you should be able to invoke these functions:
```{r binomial measures}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
